\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\begin{document}

\namesection{}{Avi Kumar Singh}{ 
\href{http://avikumar15.github.io}{{avikumar15.github.io}} | \href{mailto:avikumar.singh1508@gmail.com}{{avikumar.singh1508@gmail.com}}
}

\begin{minipage}[t]{0.31\textwidth}

\section{Education} 

\subsection{NIT, Trichy - B.Tech}

\descript{Major in Computer Science}
\descript{Minor in Economics}
\location{Expected May 2022 | Trichy, India\\ Cum. GPA: 8.30/10.00}
\sectionsep

\subsection{Devi Academy Senior}
\subsection{Secondary School}
\descript{Grad. April 2016 | Chennai}
CBSE : CGPA - 10.0/10.0 \\
\descript{Grad. April 2018 | Chennai}
CBSE : 93.6 \%
\sectionsep

\section{Links} 
\textbf{GitHub}: \href{https://github.com/avikumar15}{@avikumar15} \\
\textbf{LinkedIn}: \textbf{\href{https://www.linkedin.com/in/avi-kumar-singh-1508}{@avi-kumar-singh-1508}} \\
\textbf{Codeforces}: \textbf{\href{https://codeforces.com/profile/avikumar15}{@avikumar15}}  \\
\textbf{HackerRank}:  \textbf{\href{https://www.hackerrank.com/avikumar15?hr_r=1}{@avikumar15}}  \\
\sectionsep

\section{Coursework}
Data Structure \& Algorithms \\
Database Management System \\
Machine Learning \\
Artificial Intelligence \\
Operating System \\
Formal Languages and Automata \\ 
Combinatorics Graph Theory \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Skills
% \section{Skills}
% \subsection{Technical Skills}
% \descript{Programming Languages}
% Python \textbullet{} C++ \textbullet{} Java \textbullet{} Kotlin \textbullet{} JavaScript \textbullet{} TypeScript \textbullet{} Go \\
% \vspace{2mm}
% \descript{Web Development}
% HTML \textbullet{} CSS \textbullet{} React \textbullet{} Svelte \textbullet{} NodeJS \textbullet{} Flask \textbullet{} Django \\
% \vspace{2mm}
% \descript{App Development}
% Android Studio \textbullet{} Android Jetpack \\
% \vspace{2mm}
% \descript{Tools}
% Linux \textbullet{} Git \textbullet{} TensorFlow \textbullet{} \\ Docker \textbullet{} MySQL \\
% \vspace{2mm}
% \descript{Familiar}
% Machine Learning \textbullet{} Computer Vision
% \sectionsep

\section{Skills}
\descript{Programming Languages} {
\textbullet{C} \textbullet{C++} \textbullet{Java} \textbullet{Kotlin} \textbullet{Python} \\
}
\vspace{2mm}
\descript{Familiar Languages} 
\textbullet{C\#} \textbullet{Go} \textbullet{JavaScript} \\
\vspace{2mm}
\descript{Tools/Tech} 
\textbullet{CircleCI} \textbullet{Firebase} \textbullet{Game Dev} \textbullet{Git} \textbullet{JUnit Tests} \textbullet{ML} \textbullet{Mobile Dev} \textbullet{Scrapping} \textbullet{Scripts} \textbullet{Web Dev} \\
\vspace{2mm}
\descript{Misc}
\textbullet{Android Jetpack} \textbullet{gRPC} \textbullet{Coroutines} \textbullet{MVVM}

%\subsection{Android Development }
%\textbullet{} RxJava \textbullet{} Android Tests  %\textbullet{}  Canvas  \textbullet{}  SQLite  \textbullet{} MVP  \textbullet{} MVVM  \textbullet{}
%Rest APIs  \textbullet{} Dagger \textbullet{} Data Binding \textbullet{}  SharedPreferences  \textbullet{} gRPC \textbullet{} Live Data \textbullet{}  Retrofit \textbullet{}Picasso
%\sectionsep
% https://drive.google.com/file/d/1vIy0pa7z22vhjB0MadnEut0ej8C5hDI0/view

\section{Co-Curricular}
\textbullet{} \href{https://drive.google.com/file/d/1vIy0pa7z22vhjB0MadnEut0ej8C5hDI0/view}{Volunteering Exchange} to \textbf{Hanoi} \\
\textbullet{} \textbf{Team Leader} Business Development at AIESEC in NITT \\
\textbullet{} \textbf{Online mentor} of maths for underprivileged students. \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.67\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{\textbf{\href{https://www.nitt.edu/academics/departments/cse/vortex/}{Vortex}}}
\descript{| \textbf{\href{https://github.com/csea-vortex/}{WEBOPS}} | Event Coordinator }
\location{Jan 2020 – Present | NIT Trichy, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Coordinated Events of Vortex’20, the Annual National level technical symposium of CSE department, NIT Trichy. Now part of the \textbf{web operations} team.
\end{tightemize}
\sectionsep

\runsubsection{\textbf{\href{https://www.dailyobjects.com/}{DailyObjects}}}
\descript{| Application Development Internship }
\location{December 2019 – January 2020 | New Delhi, India}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Revamped the UI/UX of the \textbf{android app} at DailyObjects. Changes impacted 100,000+ app user. (\textbf{\href{https://play.google.com/store/apps/details?id=com.dailyobjects}{app-link}}) 
\item Followed a \textbf{test} driven approach to development.
\item Simplified the app codebase by using \textbf{jetpack libraries}.
\end{tightemize}
\sectionsep


\runsubsection{\textbf{\href{https://delta.nitt.edu/}{DELTA FORCE}}}
\descript{| Software Developer }
\location{July 2019 – Present | NIT Trichy, India}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Official Coding Club and \textbf{\href{https://www.nitt.edu/home/webteam/}{web-team}} of NIT Trichy. (\textbf{\href{https://delta.nitt.edu/}{Delta Force}})
\item Developed multiple android and web-apps for college fests. ( \textbf{\href{https://play.google.com/store/apps/details?id=com.pragyan20.app&hl=en}{Pragyan '20}}, \textbf{\href{https://play.google.com/store/apps/details?id=in.aaveg.aaveg2020&hl=en}{Aaveg '20}},
\textbf{\href{https://play.google.com/store/apps/details?id=com.nittfest20.app}{NITTFEST '20}}, \textbf{\href{https://play.google.com/store/apps/details?id=com.festember19.app&hl=en}{Festember '19}})  Festember'19 has \textbf{5000+ downloads}.
\item Mentored a project for Delta Winter of Code 2019-20. (\textbf{\href{https://github.com/avikumar15/photographer}{project link}})
\item Organised algos bootcamp and mentored freshers (\textbf{App and Game dev})
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Projects}

\runsubsection{Quick Mail CLI}
\descript{| Python  |  CLI  |  GitHub - \textbf{\href{https://github.com/avikumar15/quick-mail-cli}{quick-mail-cli}}  | \textbf{\href{https://pypi.org/project/quick-mail/}{PyPI}} }

\location{Dec 2020 – Jan 2021}
\begin{tightemize}
\item Developed a \textbf{command-line interface} to send mail quickly and without any hassle.
\item Utilised \textbf{argparse} and \textbf{google client library}. Followed the concept of abstraction using \textbf{zope}.
\end{tightemize}
\sectionsep

\runsubsection{Stock Price Prediction}
\descript{| ML | GitHub - \textbf{\href{https://github.com/avikumar15/ARIMA-GARCH-modeling}{ARIMA-GARCH-modeling}} }

\location{Nov 2020}
\begin{tightemize}
\item Modelled a \textbf{Machine Learning model} to predict stock prices of firms, by using \textbf{ARIMA-GARCH modeling} and \textbf{sentiment analysis} using \textbf{VADER}.
\item Achieved a \textbf{95\% accurate} model.
\end{tightemize}
\sectionsep

\runsubsection{AutoMate}
\descript{| E-Rickshaw Tracking App | Android App | Spring Boot }
\location{February 2020}

\begin{tightemize}
\item Designed a pooling based cab booking application using \textbf{Google Map API}.
\item Applied a \textbf{dijkstra based algorithm} is used which assigns rickshaw to the passenger. Factors like auto capacity, ETA, destination are considered in this algorithm.

\end{tightemize}
\sectionsep

\runsubsection{Dalal Street}
\descript{| ANDROID KOTLIN | GRPC | GO |  \textbf{\href{https://www.pragyan.org/20/projects/}{Web Link}}}
\location{September 2019 - March 2020}

\begin{tightemize}
\item Developed a \textbf{virtual stock exchange game} with backend in \textbf{Go} and \textbf{GRPC} for managing communication between backend and frontend. (\textbf{\href{https://github.com/delta/dalal-street-server}{server code}})
\item Contributed to frontend in app and web. (\textbf{\href{https://github.com/delta/dalal-street-android}{app code}}) (\textbf{\href{https://github.com/delta/dalal-street-web}{web code}})
\item Implemented \textbf{push notification}, \textbf{OTP} and \textbf{referral code}  features in app.
\end{tightemize}


% \runsubsection{UK Police App}
% \descript{| Android App | GitHub - \textbf{\href{https://github.com/avikumar15/UK-Police}{UK-Police}}}
% \location{June 2019}

% \begin{tightemize}
% \item An app to show available UK police and crime data in an organised manner.
% \item App makes API call to \textbf{\href{https://data.police.uk/}{UK Police}} data.
% \item App implements concepts of REST API, recycler view, SQLite, Fragments, SharedPreferences, and Swipe Gestures.
% \end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Volunteering Experience}

%\runsubsection{Vietnam Youth Icon - 14}
%\descript{| Teaching Professional }
%\location{December 2018 – January 2019 | Hanoi, Vietnam }
%An amazing 6 week long volunteering experience of being a part of VYI-14. The project gave me the opportunity to get out of my safe comfort zone and also make an impact on the youth of Hanoi. The exchange program also allowed me to develop my team working and leadership skills.
%\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Awards} 
\begin{tabular}{rll}
2020&Top 7 teams/ 50 teams& Transfinitte'20 organised by NITT\\
2020&Top 250 teams/ 2500 teams& Hackverse'20 organised by NITK\\
2018&Top 8 teams/ 200 teams & Qualified for NumPy second round

\end{tabular}
\sectionsep


\end{minipage} 
\end{document}
